---
title: "Assignment Machine Learning"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

The goal of this project is to predict the manner in which 6 people exercise.
This is the "classe" variable in the training set. Other variables were used to predict, in order to
create a model and to perform the prediction of 20 different test cases.


## Process

First it was neccesary to load the files, this files were readed using the comand csv. considering that the NAS had a different form ("#DIV/0!")

```{r echo=FALSE}
#Set directory
setwd("C:/Users/Rafaela Becerra/Desktop/Coursera/Practical Machine Learning")

#Load all the packages that might be needed
library(caret)
library(randomForest)
```

I prove a few methods but I decided to use the Random Forest algorithm because it was the better fit and proved the more accuracy, sensitivity & specificity.I used set.seed to make my work reproducible.
```{r  eval=FALSE, echo=TRUE}
set.seed(50000)

#Read the training data
training <- read.csv("pml-training.csv", stringsAsFactors=FALSE, na.strings=c("NA", "#DIV/0!"))

#Change NAS with 0
training[is.na(training)]<-0

#Split the data in testing ad training with a 75/25
inTrain <- createDataPartition(y=training$classe, p=0.75, list=FALSE)
training <- training[inTrain,]
testing <- training[-inTrain,]
```
I drop variables that are not necesary: X, user_name, raw_timestamp_part_1, raw_timestamp_part_2,
cvtd_timestamp, new_window, num_window and the ones that have near to cero variance.
```{r eval=FALSE, echo=TRUE}
training <- training[,-(1:7)]
training <- training[,-nearZeroVar(training)]
```
I used a random forest wich gave me an accuracy of 0.97 by evaluating it with the use of the confusionmatrix method 
```{r eval=FALSE, echo=TRUE}
modelFit <- randomForest(classe ~., data=training, type="class")
confusionMatrix(modelFit)
```
The code used for presenting the prediction for the 20 cases was
```{r eval=FALSE, echo=TRUE}
testing <- read.csv("pml-testing.csv", stringsAsFactors=FALSE, na.strings=c("NA", "#DIV/0!"))

#For predinting the model I run this code
test <- predict(modelFit, newdata = testing, type="class")
```

